netcdf_to_brick_projected

### 2018-10-22 src/netcdf_to_brick_projected.Rmd
raster brick loop with projection done. working on first stages of extraction

@@

Ok first get a list of netcdfs in the folder...
```{r}
netcdf_list <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = TRUE)
netcdf_list
```

ok now create a raster brick for each netcdf (with the same file name),

```{r}
no_netcdf <- length(netcdf_list)
netcdf_name <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf) {
  print(netcdf_name[i]) #this just prings the name of the netCDF R is working on
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  assign(netcdf_name[i], temp_brick) #this asigns the netCDF name to the raster brick
}

```

>>>>

SAM - YOU MIGHT WANT TO [PARALLEL PROCESS FOR THE WHOLE DATASET..](https://cran.r-project.org/web/packages/doParallel/vignettes/gettingstartedParallel.pdf) and also [here](https://gis.stackexchange.com/questions/253618/r-multicore-approach-to-extract-raster-values-using-spatial-points)

@@

Ok first get a list of netcdfs in the folder...
```{r}
netcdf_list <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = TRUE)
```

ok now create a raster brick for each netcdf, project, and assing the same file name as the netCDF

```{r}
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf) {
  print(netcdf_name[i]) #this just prings the name of the netCDF R is working on
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) #aea is an existing raster in the projection I want that I created (environmental_data_preperation)
  assign(netcdf_name[i], temp_brick) #this asigns the netCDF name to the raster brick
}

```
just a quick test....

```{r}
`1998_01_salinity.nc`
plot(`1998_01_salinity.nc` [[8]])
```

Look up year and month in the occurence data (data_aea)
year = data_aea$year
month = data_aea$month

the raster brick file names are 
character 1:4 = year
charcater 6:7 = month
character 9:end = env. variable name

maybe start by splitting the occurence data into year-month? Then you can search for the rasters without going through everything....
```{r}
species_obs_date <- split(data_aea,paste(data_aea$year, data_aea$month))
species_obs_date
```
